Analysis for Biracial Grade Retention Project

### 2021-11-24 analysis/analysis.Rmd
Add code folding to analysis.Rmd output

---
title: "Analysis for Biracial Grade Retention Project"
output: 
  rmdformats::robobook:
    highlight: tango
    toc_depth: 2
    fig_height: 6
    fig_width: 9
---

>>>>

---
title: "Analysis for Biracial Grade Retention Project"
output: 
  rmdformats::robobook:
    highlight: tango
    toc_depth: 2
    fig_height: 6
    fig_width: 9
    code_folding: hide
---
